```{r}
rm(list = ls())

PAQUETES <- c("dplyr","tidyverse","ggplot2","readxl","network3D")

for (el in PAQUETES){
  if (!require(el, character.only = TRUE)) {
    install.packages(el)
    require(el, character.only = TRUE)
  }
}

if(!require(networkD3)) install.packages("networkD3")
library(networkD3)

rm(PAQUETES, el)
```
Read INE excel values
```{r}
recursos<- read_excel("./1.data/S_1.xlsx",sheet="operaciones_y_saldos",range="B8:CY37")
recursos<-recursos[-(1:3),-2]

colnames(recursos)[1]<-"code"
colnames(recursos)[2]<-"name"

recursos %>% 
  rowwise() %>% 
  mutate(values_2022 = sum(as.numeric(c_across(contains("2022"))),na.rm=T)) %>% 
  select(code,name,values_2022) -> recursos
recursos$type<-"Recursos"


empleos<- read_excel("./1.data/S_1.xlsx",sheet="operaciones_y_saldos",range="B39:CY78")

colnames(empleos)
empleos<-empleos[-(1:3),-2]

colnames(empleos)[1]<-"code"
colnames(empleos)[2]<-"name"
empleos %>% 
  rowwise() %>% 
  mutate(values_2022 = sum(as.numeric(c_across(contains("2022"))),na.rm=T)) %>% 
  select(code,name,values_2022) -> empleos
empleos$type<-"Empleos"


saldos<- read_excel("./1.data/S_1.xlsx",sheet="operaciones_y_saldos",range="B80:CY97")

colnames(saldos)
saldos<-saldos[-(1:3),-2]

colnames(saldos)[1]<-"code"
colnames(saldos)[2]<-"name"
saldos %>% 
 rowwise() %>% 
  mutate(values_2022 = sum(as.numeric(c_across(contains("2022"))),na.rm=T)) %>% 
  select(code,name,values_2022) -> saldos
saldos$type<-"saldo"


# merge the 3 dataframes

values <-rbind(recursos,empleos,saldos)


values %>% mutate(values_2023=values_2022) %>% 
  mutate(values_2022=values_2023) %>% 
  select(-values_2023) -> values

```

# now load data for rest of the world
```{r}
recursos_RoW<- read_excel("./1.data/S_2.xlsx",sheet="operaciones_y_saldos",range="B8:CY39")
recursos_RoW<-recursos_RoW[-(1:3),-2]

colnames(recursos_RoW)[1]<-"code"
colnames(recursos_RoW)[2]<-"name"

recursos_RoW %>% 
  rowwise() %>% 
  mutate(values_2022 = sum(as.numeric(c_across(contains("2022"))),na.rm=T)) %>% 
  select(code,name,values_2022) -> recursos_RoW
recursos_RoW$type<-"Recursos"


empleos_RoW<- read_excel("./1.data/S_2.xlsx",sheet="operaciones_y_saldos",range="B41:CY80")

colnames(empleos_RoW)
empleos_RoW<-empleos_RoW[-(1:3),-2]

colnames(empleos_RoW)[1]<-"code"
colnames(empleos_RoW)[2]<-"name"
empleos_RoW %>% 
  rowwise() %>% 
  mutate(values_2022 = sum(as.numeric(c_across(contains("2022"))),na.rm=T)) %>% 
  select(code,name,values_2022) -> empleos_RoW
empleos_RoW$type<-"Empleos"


saldos_RoW<- read_excel("./1.data/S_2.xlsx",sheet="operaciones_y_saldos",range="B82:CY89")

colnames(saldos_RoW)
saldos_RoW<-saldos_RoW[-(1:3),-2]

colnames(saldos_RoW)[1]<-"code"
colnames(saldos_RoW)[2]<-"name"
saldos_RoW %>% 
 rowwise() %>% 
  mutate(values_2022 = sum(as.numeric(c_across(contains("2022"))),na.rm=T)) %>% 
  select(code,name,values_2022) -> saldos_RoW
saldos_RoW$type<-"saldo"


# merge the 3 dataframes

values_RoW <-rbind(recursos_RoW,empleos_RoW,saldos_RoW)
values_RoW %>% mutate(values_2023=values_2022) %>% 
  mutate(values_2022=values_2023) %>% 
  select(-values_2023) -> values_RoW

```
Cargo contabilidad anual para los componentes de demanda
```{r}

cont_anual <- read_excel("./1.data/pib95_22.xlsx",sheet="Tabla_1",range="B10:BG33")
colnames(cont_anual)[2]<-"name"
cont_anual %>%
  select(name,"2022 (A)") %>%
  mutate(code="CA") %>%  #para el join
  rename(values_2022_demanda="2022 (A)") -> cont_anual
```



load flux
```{r}
flux<-read_excel("./1.data/S_1.xlsx",sheet="flujo")
flux %>% 
  left_join(values,by=c("code","name","type")) %>% 
  left_join(cont_anual,by=c("name","code")) %>%
  mutate(values_2022=coalesce(values_2022, values_2022_demanda)) %>% #coalesce merges two columns where there are nas
  select(-values_2022_demanda) %>%
  #replace long name in transferencias de capital
  mutate(name = if_else(str_detect(name, "Transferencias de capital"), "Transferencias de capital", name)) %>% 
    select(code,name,type,account,direction,values_2022,RM, order)->flux


```

We need to recalculate those flux that goes partly to rest of the world
```{r}
#get values that interact with RoW
flux %>% 
  filter(RM=="Y") %>% 
  select(-RM) -> RoW_accounts


#get the rows from the RoW df
values_RoW %>% 
  filter(code %in% RoW_accounts$code) %>% 
  filter(code != "D.3") %>% #subvenciones on their own
  mutate(name = case_when(
            code =="D.9" ~ "Transferencias de capital",
            T ~ name
        ),
        type= case_when(
            code =="D.9"&type=="Recursos" ~ "Empleos",
            code =="D.9"&type=="Empleos" ~ "Recursos",
            T ~ type
        )
        ) %>% 
  left_join(RoW_accounts %>% select(code,type,account,order),by=c("code","type")) %>% 
  mutate(name=case_when(
      type == "Recursos" ~ paste0(name, " recibidas de RM"),
      type == "Empleos" ~ paste0(name, " pagadas a RM"),
      T ~ name
      ),
    direction=type
  ) %>% 
  arrange(order,code,name) -> RoW_flux

#Substract flux to RoW from accounts
RoW_accounts %>% 
  arrange(order,code,name) %>% 
  filter(code != "D.3") %>%
  mutate(values_2022=values_2022-RoW_flux$values_2022) %>% 
  rbind(RoW_flux) ->RoW_accounts

#for subvenciones
values_RoW %>% 
    filter(code == "D.3") %>% 
  left_join(RoW_accounts %>% select(code,type,account,order),by=c("code","type")) %>% 
  unique() %>% 
  mutate(type=case_when(
    type=="Recursos" ~ "Empleos",
    type == "Empleos" ~ "Recursos"
  ),
   direction=type
  ) %>%
  arrange(order,code,type)->subvenciones_RoW

flux %>% 
  filter(code=="D.3") %>% #sbvenciones 
  select(-RM) %>% 
  arrange(code,type) %>% 
  mutate(values_2022=values_2022-subvenciones_RoW$values_2022,
         values_RoW=subvenciones_RoW$values_2022) %>% 
  pivot_longer(c(values_2022,values_RoW),names_to="RoW",values_to = "values_2022") %>% 
  mutate(name=case_when(
    type=="Recursos" & RoW=="values_RoW" ~ "subvenciones recibidas del RM",
    T~name)
    ) %>% 
  filter(values_2022>0) %>% 
  select(-RoW) %>% 
  mutate(type=case_when(
    type=="Recursos" & code == "D.3" ~ "Empleos", #swap direction of subvenciones RoW
    type == "Empleos" & code == "D.3" ~ "Recursos"
  ))->subvenciones

# paste into flux df
flux %>% 
  filter(is.na(RM),
        code != "D.3") %>% 
  select(-RM) %>% 
  rbind(RoW_accounts,subvenciones) %>% 
  arrange(code,direction)->flux
```

tenemos que dar la vuelta segun sean recursos o empleos
```{r}
flux %>% 
  filter(direction=="Recursos") -> flujo_recursos
flux %>% 
  filter(direction=="Empleos") -> flujo_empleos

flujo <-data.frame(
  Source=c(pull(flujo_recursos,name),pull(flujo_empleos,account)),
  target=c(pull(flujo_recursos,account),pull(flujo_empleos,name)),
  values=c(pull(flujo_recursos,values_2022),pull(flujo_empleos,values_2022)),
  order=c(pull(flujo_recursos,order),pull(flujo_empleos,order))
) %>% 
  # arrange(order) %>% 
  select(-order)

```

swap the target and value for negative values
```{r}
 flujo %>%  mutate(new_source = if_else(values < 0, target, Source),
         new_target = if_else(values < 0, Source, target),
         Source = new_source,
         target = new_target,
         values =if_else(values<0,-values,values)) %>% # to positive 
  select(-new_source, -new_target) ->flujo

nodes<-data.frame(
  names=c(pull(flujo,Source),pull(flujo,target),paste0("FALSO",seq(1,17))) %>% unique()
)
```

creo flujos falsos de 0 para modificar el grafico
NO, BUGEAN EL GRAFICO
```{r}
# 
# falsos<-data.frame(Source=paste0("FALSO",seq(1,16)),
#                    target=paste0("FALSO",seq(2,17)),
#                    values=c(0)
# )
# #add links to real flux
# add_falsos <-data.frame(Source=c("FALSO11","FALSO7"),
#                         target=c("Exportaciones de bienes y servicios",
#                                  "Adquisiciones menos cesiones de activos no producidos"
#                                 ),
#                         values=c(0,0)
#                   )
# 
# flujo <-rbind(flujo,falsos,add_falsos)
```

```{r}
write_csv(nodes,"1.data/nodes.csv")

nodes<-read_excel("./1.data/nodes_dict.xlsx") %>% data.frame() %>% 
  replace_na(list(new_names="\ "))
             
```


```{r}



source_index<-list()
ii<-1
for (element in flujo$Source) {
  indices <- which(nodes$names == element)
  source_index[[ii]] <- indices-1
  ii<-ii+1
}

target_index<-list()
ii<-1
for (element in flujo$target) {
  indices <- which(nodes$names == element)
  target_index[[ii]] <- indices-1
  ii<-ii+1
}

#create links dataframe
links<-flujo %>%
  mutate(source=as.numeric(source_index),
         target=as.numeric(target_index)
         )%>%
  select(-Source) 

links$colors<-nodes$new_names[links$source + 1]

# myColors <- 'd3.scaleOrdinal().domain(["M", "W"]) .range(["#5485AB", "#BA4682"])'
# Create the Sankey diagram
sankey <- sankeyNetwork(Links = links, 
                        Nodes = nodes, 
                        Source = "source", 
                        Target = "target", 
                        Value = "values", 
                        NodeID = "new_names",
                        units = 'Millones de Euros', 
                        fontSize = 20, 
                        nodeWidth = 15,
                        colourScale ="d3.scaleOrdinal(d3.schemeCategory20);",
                        sinksRight=F,
                        nodePadding = 10,
                        # LinkGroup = "colors",
                        iterations = T, #allows to manual order of nodes as in the nodes df
                         height = 1500, 
                         width = 3000,
                        )



print(sankey)

?sankeyNetwork()
?sankeyNetworkOutput()

```

```{r}
URL <- paste0('https://cdn.rawgit.com/christophergandrud/networkD3/',
              'master/JSONdata/energy.json')
energy <- jsonlite::fromJSON(URL)

energy$links$energy_type <- sub(' .*', '',
                               energy$nodes[energy$links$source + 1, 'name'])
```

